ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating section Functionalities
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

Through the integration of COM into ESBMC ({\it i.e.}, ESBMC-GPU), one is able to analyze CUDA programs and verify the following properties: data-race conditions, in order to detect if multiple threads perform unsynchronized access to shared-memory locations; pointer safety, {\it i.e.}, whether {\it (i)} a pointer offset does not exceed object bounds and {\it (ii)} a pointer is neither {\tt NULL} nor invalid; array bounds, in order to ensure that array indices are within known bounds; arithmetic under- and overflow, which happens when a sum or product exceeds the memory limits that a variable can handle; division by zero, which takes place when denominators, in arithmetic expressions, lead to a division by zero; and user-specified assertions, {\it i.e.}, all assertions specified by users, which is essential to a thorough verification process.%, as some specific possible violations must be explicitly pointed out.

>>>>

Through the integration of COM into ESBMC ({\it i.e.}, ESBMC-GPU), one is able to analyze CUDA programs and verify the following properties: data-race conditions, in order to detect if multiple threads perform unsynchronized access \textcolor{blue}{to the same memory locations}; pointer safety, {\it i.e.}, whether {\it (i)} a pointer offset does not exceed object bounds and {\it (ii)} a pointer is neither {\tt NULL} nor invalid; array bounds, in order to ensure that array indices are within known bounds; arithmetic under- and overflow, which happens when a sum or product exceeds the memory limits that a variable can handle; division by zero, which takes place when denominators, in arithmetic expressions, lead to a division by zero; and user-specified assertions, {\it i.e.}, all assertions specified by users, which is essential to a thorough verification process.%, as some specific possible violations must be explicitly pointed out.
